### 2020-01-16 Article.tex
Maxo acaba ya

During this section we want to study
the asymptotic probability that the 
$r$-neighborhood of a given vertex $v\in \N$
in $G_n$ 
is a tree that belongs to a given $k$-equivalence
class of trees $\mathcal{T}$ with radius at most
$r$. That is, we want to know
\[\Ln \mathrm{Pr}\big( 
T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
\]
Denote this limit by $\mathrm{Pr}[\mathcal{T}]$. Notice that the definition of  $\mathrm{Pr}[\mathcal{T}]$ does not depend by the
choice of $v$.\\

An easy observation is that if we are given a finite
set of vertices $X \subset \N$ and some

vertex $v\in \N$ and a $k$-equivalence class
of trees $\mathcal{T}$ with radius at most $r$,

In this section we want to show that, given various classes of
$k$-equivalence over rooted trees of radii at most $r$,
$\mathcal{T}_1,\dots,\mathcal{T}_l$, and for 
any fixed vertices $v_1,\dots,v_l \in \N$,
the limit probabilities that each $N(v_i;r)$ is a tree which
belongs to $\mathcal{T}_i$ class when rooted at $v_i$ are
independent and they vary analitically with $\overbar{\beta}$.\par

%During this section we will consider
%inside of $G_n$ a set of distinguished vertices
%$\overbar{v}\in \N*$ cho

>>>>

During this section we want to study
the asymptotic probability that the 
$r$-neighborhood of a given vertex $v\in \N$
in $G_n$ 
is a tree that belongs to a given $k$-equivalence
class of trees $\mathcal{T}$ with radius at most
$r$. That is, we want to know
\[\Ln \mathrm{Pr}\big( 
T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
\]
Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
definition of  $\mathrm{Pr}[r,\mathcal{T}]$ does not depend by the
choice of $v$.\par

We define $\Lambda$ and $M$ as the minimal families
of expressions with arguments $\overbar{\beta}$ that satisfy
 the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
for any $b,i\in \N$ with $1\leq i \leq c$,
$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
the expression $(\beta_i/b) \prod_{j=1}^{a_i-1}\lambda_j$
belongs to $M$,  \textbf{(3)}
for any $\mu\in M$ and any $n\in \N$ both
$\mathrm{Poiss}_{\mu}(n)$ and $\mathrm{Poiss}_\mu(\geq n)$ are in $\Lambda$, 
and  \textbf{(4)} for any $\lambda_1,\lambda_2 \in \Lambda$, the
product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
\par
The goal of this section is to show  want to 
show that $\mathrm{Pr}[r,\mathcal{T}]$,
as an expression with parameters
$\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
$r$ and $\mathcal{T}$. The argument is as follows:
let $T:=N^{G_n}(v;r)$. \par

\begin{lemma}
	Let $X\subset \N$ be a finite set of fixed vertices, and let 
	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
	$r+1$ between any two vertices $u,v\in X$, and (2)
	a.a.s $G^\prime_n$ does not contain a cycle containing
	any vertex $u\in X$.
\end{lemma}
\begin{proof}
	To prove the first part of the statement it suffices
	to show that the expected number of such paths
	tends to zero as $n$ tends to infinity. 
	Let $P$ be a path of size $r+1$ between two vertices $w,z$,
	and let $u,v$ be two vertices from $X$. 
	Given $f$ 	
\end{proof}

Let $\overbar{v}\in \N*$ a list of vertices. For each $n,r\in \N$ and 
$v_i\in \overbar{v}$ we define the random hypergraph
$T_n(v_i,\overbar{v};r)$ in the following way: Let $G^\prime_n:=G_n \setminus
E(G_n[\overbar{v}])$. Then $T_n(v_i,\overbar{v};r):= N^{G^\prime_n}(v;r)$.
That is, $T_n(v_i,\overbar{v};r)$ is the $r$-neighborhood of $v_i$ in ``$G_n$
minus the edges induced on $\overbar{v}$".

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\overbar{v}\in \N*$ be another list of 
		 Let $r_1,\dots r_k\in \N$ and let
		$\mathcal{T}_1,\dots \mathcal{T}_k$ be 
		$k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Let
		$\overbar{v}$ denote a list of fixed vertices 
		$v_1,\dots,v_k,\dots, v_l\in \N$, and let 
		$\phi(\overbar{x})$ be an open sentence on $l$ variables.
		Let $G_n^\prime=G_n\setminus E[\overbar{v}]$ 
	\end{itemize}

Let $\overbar{\mathcal{T}}$ be a  $\overbar{u}\in N$

\end{theorem}
%During this section we will consider
%inside of $G_n$ a set of distinguished vertices
%$\overbar{v}\in \N*$ cho
